Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Clean up and rename images for consistency
- Removes unused images and renames existing ones for clarity and consistency.
- Updates references across files to match new image names, ensuring cohesive project presentation.

![](img/SoundPulseLogo.png){width="100%"}
:::
::::

@@

::: {.absolute top="80%" left="12%" width="80%"}
<!-- TODO: exchange for gif -->
![](img/before-bid.png)
:::

@@

::: {.r-stack style="text-align:center"}
![](img/Screenshot_examples_reactable_1.png){width="100%"}

![](img/Screenshot_examples_reactable_2.png){.fragment width="100%"}

![](img/Screenshot_examples_reactable_3.png){.fragment width="100%"}

![](img/Screenshot_examples_reactable_4.png){.fragment width="100%"}

![](img/Screenshot_examples_reactable_5.png){.fragment width="100%"}
:::

@@

::: {.r-stack style="text-align:center"}
![](img/Screenshot_examples_echarts4r_1.png){width="75%"}

![](img/Screenshot_examples_echarts4r_2.png){.fragment width="75%"}

![](img/Screenshot_examples_echarts4r_3.png){.fragment width="75%"}

![](img/Screenshot_examples_echarts4r_4.png){.fragment width="75%"}
:::

>>>>

![](img/soundpulse-logo.png){width="100%"}
:::
::::

@@

::: {.absolute top="80%" left="12%" width="80%"}
<!-- TODO: exchange for gif? -->
![](img/before-bid.png)
:::

@@

::: {.r-stack style="text-align:center"}
![](img/reactable-ex1.png){width="100%"}

![](img/reactable-ex2.png){.fragment width="100%"}

![](img/reactable-ex3.png){.fragment width="100%"}

![](img/reactable-ex4.png){.fragment width="100%"}

![](img/reactable-ex5.png){.fragment width="100%"}
:::

@@

::: {.r-stack style="text-align:center"}
![](img/echarts4r-ex1.png){width="75%"}

![](img/echarts4r-ex2.png){.fragment width="75%"}

![](img/echarts4r-ex3.png){.fragment width="75%"}

![](img/echarts4r-ex4.png){.fragment width="75%"}
:::
